Hierarchical Controller Architecture for SDN

### 2013-11-05 presentation/ppt.tex
future work, hitches, timestamp, references

\frame{
\frametitle{Our Approach}
\begin{itemize}
\item What is being done ? 
	\begin{itemize}
		\item It's a Replicated state machine (strong or lazy replication) architecture, which had been well studied in Distributed Systems community
		\item Past work uses DHTs (Onix), Transactional DB (Onix), DFS (Hyperflow)
	\end{itemize}
	\item We are trying to study		
	\begin{itemize}
		\item Instead of using a general repilication mechanism, can we exploit the fact that network views are being replicated ?
		\item Could the SDN datapath (replication client) make use of replication timestamps ?
	\end{itemize}

@@

\frame{
\frametitle{Timestamp}
	\begin{itemize}   
		\item Handle domain level inconsistencies in Domain Network
		\item Each domain i maintains a vector timestamp, conistsing of revision number of domains
		\item Border routers in a domain may change a flow depending on it's timestamp
	\end{itemize}   
}

@@

\frame{
\frametitle{Future Work}
\begin{itemize}
	\item 
	\item Implement using OpenFlow
\end{itemize}
}

\frame{
	\frametitle{Hiccups}

\frame{
\centerline{Thank you!}
Suggestions and Questions are welcome, suggestions a little more than questions
}

>>>>

\frame{
\frametitle{Our Approach}
\begin{itemize}
\item What is being done ? 
	\begin{itemize}
		\item It's a Replicated state machine (strong or lazy replication) architecture, which had been well studied in Distributed Systems community
		\item Past work uses DHTs (Onix), Transactional DB (Onix), DFS (Hyperflow)
	\end{itemize}
	\item We are trying to study		
	\begin{itemize}
		\item Instead of just using a general repilication mechanism, can we exploit the fact that network views are being replicated ?
		\item Could SDN datapath (replication client) make use of replication timestamps ?
	\end{itemize}

@@

\frame{
\frametitle{Timestamp}
	\begin{itemize}
		\item An example - Link Balancer Controller [4]
		\item On a flow arriving at an ingress port, a path with minimum maximum utilization is choosen
		\item Each domain i maintains a vector timestamp, conistsing of revision number of domains' link utilizations, seen so far
		\item When a flow path is set up at a domain, it is augmented by the timestamp of the domain
		\item Border routers in a domain may change a flow path if their timestamp is greater than flow's timestamp
		\item Flow's timestamp is updated as it passes through domains
		\item what if flow's timestamp is neither greater nor smaller than domain's timestamp ?
	\end{itemize}   
}

@@

\frame{
\frametitle{Hitches}
\begin{itemize}
	\item Hierarchical Architecture
	\begin{itemize}
		\item Suboptimal performance
	\end{itemize}
	\item Network Aggregation
	\begin{itemize}
		\item May backfire: single internal update may cause multiple updates in aggregated network 
	\end{itemize}
	\item Timestamps
	\begin{itemize}
		\item Not a true datapath technique
		\item Improve the performance of control applications, however, does not provide any guarantees
	\end{itemize}
\end{itemize}	
}

\frame{
\frametitle{Future Work}
\begin{itemize}
	\item Understand the trade-off between sub-optimality and frequency of updates, in case of hierarchical architecture
	\item Revise Network Aggregation data structures so as not to explode network updates
	\item Implement and simulate each approach on real ISP topology with real traffic data. Analyze performance
\end{itemize}
}

\frame{
\centerline{Thank you!}
}

\frame{
\frametitle{References}
\begin{itemize}
\item [1] T. Koponen, M. Casado, N. Gude, J. Stribling, L. Poutievski, M. Zhu, R. Ramanathan, Y. Iwata, H. Inoue, T. Hama, and S. Shenker. Onix: a distributed control platform for large-scale production networks. In Proceedings of the 9th USENIX OSDI conference , pages 1 - 6, 2010.
\item [2] A. Tootoonchian and Y. Ganjali. Hyperflow: a distributed control plane for openflow. In Proceedings of the 2010 INM conference, 2010.
\item [3] Soheil Hassas Yeganeh and Yashar Ganjali. Kandoo: a framework for efficient and scalable offloading of control applications. In Proc. 1st Workshop on Hot Topics in Software Defined Networking (HotSDN 2012), pages 19-24, New York, 2012. ACM Press. 
\item [4] D. Levin, A. Wundsam, B.Heller, N. Handigol, and A. Feldmann, Logically Centralized State Distribution Trade-offs in Software Defined Networks  in HotSDN, 2012. 
\end{itemize}
}

\frame{
\begin{itemize}
\frametitle{References}
\item [5] Stefan Schmid and Jukka Suomela, Exploiting Locality in Distributed SDN Control, in HotSDN, 2013. 
\item [6] Advait Dixit, Fang Hao, Sarit Mukherjee, T. V. Lakshman and Ramana Kompella, Towards an Elastic Distributed SDN Controller, in HotSDN, 2013.
\item [7] Nate Foster, Rob Harrison, Matthew L. Meola, Michael J. Freedman, Jennifer Rexford and David Walker, Frenetic: A High-Level Language for OpenFlow Networks. ACM PRESTO 2010.
\end{itemize}
}
